Visualization of [fulle name] Fractional Integrals

### 2019-04-12 fractional/CMJ style files/article-template.tex
added extra text to article

We can assign a geometric interpretation to the above fractional integrals by converting them into Cavalieri integrals. This can be achieved by first 
converting the above integrals into Riemann-Stieltjes integrals and then converting the resulting integrals into Cavalieri integrals. Exaclty how these conversion are 
to be performed is discussed in the previous section. The inegrator $g_t^{\alpha}(\tau)$ of the aforementioned intermediate Riemann-Stieltjes integrals are equal and independent of the integrand $f(\tau)$.
The set of functions $\{g_{10}^{\alpha}(\tau)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ are presented in Table \textbf{??}. The integration limits of the aformentioned Cavalieri 
integrals are functions and are determined by the integrand $f(\tau)$ and the integrator $g_t^{\alpha}(\tau)$. The shape of the infini

>>>>

We can assign a geometric interpretation to the above fractional integrals by converting them into Cavalieri integrals. This can be achieved by first 
converting the above integrals into Riemann-Stieltjes integrals and then converting the resulting integrals into Cavalieri integrals. Exaclty how these conversion are 
to be performed is discussed in the previous section. The inegrator $g_t^{\alpha}(\tau)$ of the aforementioned intermediate Riemann-Stieltjes integrals are equal and independent of the integrand $f(\tau)$.
The set of functions $\{g_{10}^{\alpha}(\tau)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ are presented in Table \textbf{??} and depicted in Figure\textbf{??}. The integration limits of the aformentioned Cavalieri 
integrals are functions and are determined by the integrand $f(\tau)$ and the integrator $g_t^{\alpha}(\tau)$. The set of functions $\{a_{10}^{\alpha}(y)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ that can be 
associated with the integrals in Eq~{??} and Eq~{??} are presented in Table~\textbf{??}. Note that neither $g_t^{\alpha}(\tau)$ nor $a_t^{\alpha}(y)$ are static functions, 
they depend on the value of $\alpha$ and $t$. This implies that a fractional integral of order $\alpha$ and extent $t$ can be interpeted as an infitesimal sum of an infinite number of infinitesimals whose 
shape is determined by $\alpha$ and $t$.

To make things clearer lets set the value of $\alpha$ to $0.8$ and the value of $t$ to 10 and then depict the region associated that is associated with the Cavalieri integral which is obtained

the obtained Lets depict the geometric interpretation

%The integration limits of the aformentioned Cavalieri 
%integrals are functions and are determined by the integrand $f(\tau)$ and the integrator $g_t^{\alpha}(\tau)$. Recall that a Cavalieri integral can 
%be interpreted as an infinite sum of non-rectanguar infinitesimals whose shape is determined by its lower integration limit $a_t^{\alpha}(y)$. The set of functions 
%$\{a_{10}^{f,\alpha}(y)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ that can be associated with the integrals in Eq~{??} and Eq~{??} are presented in Table~\textbf{??}. Note that 
%$a_t^{\alpha}(y)$ is not a static function it depends on the order of integration $\alpha$ and the integration limit $t$. The fact that $a_t^{\alpha}(y)$ is dependend 
%on $t$ implies that a fractional integral of a particular order cannot be converted to a single Cavalieri integral, but rather to an infinite set $\mathcal{C}$ of Cavalieri integrals.
%Each element of $\mathcal{C}$ is associated with a particular choice of $t$. Let $\mathcal{B}_f = \{b_{t}^{f,\alpha}(y)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$. In Fig.~\ref{fig:geo1} and Fig.~\ref{fig:geo2} we plot the elements of $\mathcal{B}$. 
%The brigther the function the larger $t$ is. For the case $t=10$ we also plot the integration strips. The fractional integral $\frac{1}{\Gamma(\alpha)}\int_0^10 f(\tau) (t-\tau)^{\alpha-1}~d\tau$ can therefore 
%be interpreted as the sum of inThey clearly do not match the other functions.

\begin{enumerate}
 \item Examples.
 \item If we evaluate \textbf{[is this word correct?]} these integrals we obtaine the functions in Table \textbf{??}. These functions are plotted in Fig xx.
 \item Assign a geometric interpretation by converting to a Riemann-Stieltjes integral and then to a Cavalieri integral.
 \item \textbf{[Is there a need to mention the fact that it is mapped to a set of different Cavalieri integrals]}. Note that we obtain a different 
 Cavalieri integral for each value of alpha and t.
 \item Let us fix alpha and t to specific values, ie write down the integrals. The function b the left most function in the leftmost panel (plotted in the lightest 
 shade of gray of all the y-valued functions. The integral , and by implication , can be inerpreted as the are of the region formed by f, b and the x-axis. This 
 area can be obtained by summing together an infinite number of infinitesimals whose shape is determined by b. This are can be approximated by using integration strips. These 
 strips is depicted using dashed lines. The area of this region and $t$ forms a specific point on the curves in Fig. The point is plotted in the same shade of gray than b.
 \item If we take another value of t we obtain a different region. Note that b and b are not mere translations of each other. Changing the integration limit alters the 
 shape of the infinitesimal we need to use. Althoug both t and alpa alters the shape of b, it is only alpha that fundamentally changes .... \textbf{[how to state this shape altering thing i do not know]} 
 \item Need to finish the discussion of al the points mapping to the other figures. 
 \item Summary of overall interpretation of fractional integral.....
\end{enumerate}

\begin{figure}[htb]
\centering
\includegraphics[width=1\textwidth]{geo_int1.pdf}
\caption{A plot of $\Gamma(x)$. $\Gamma(x)$ is not defined for the non-negative integers.}
\label{fig:geo1}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=1\textwidth]{geo_int2.pdf}
\caption{A plot of $\Gamma(x)$. $\Gamma(x)$ is not defined for the non-negative integers.}
\label{fig:geo2}
\end{figure}
